The K2 Bright Star Survey

### 2019-05-15 paper/ms.tex
fix syntax

% do hot star asteroseismology and red giants as benchmarks, interferometry
Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.) and the Hyades giants (White et al., in prep.). In addition to this, we aim to separately publish asteroseismic catalogues of the red giants (Yu et al., in prep.) and main-sequence stars (Greklek-McKeon et al., in prep.).

% do k2 smear after that
The sample of K2 bright stars presented here only includes those with halo apertures, but while some others are available conventionally, many were not assigned target pixels and were not downloaded at all. Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., in prep.), and this can also be done in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more challenging. A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.

>>>>

% do hot star asteroseismology and red giants as benchmarks, interferometry
Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.), the Hyades giants (White et al., in prep.), and main-sequence stars (Greklek-McKeon et al., in prep.).

% do k2 smear after that
The sample of K2 bright stars presented here only includes those with halo apertures, but while some others are available conventionally, many were not assigned target pixels and were not downloaded at all. Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., under review), and this can also be done in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more challenging. A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.
